Supplement

### 2023-02-16 06_Paper/ER-ED/ERED_Stage2/Supplement.Rmd
created separate file for supplement

---
title             : "Estimating individual subjective values of emotion regulation strategies"
shorttitle        : "Subjective values of emotion regulation strategies"
author:
  - name          : "Christoph Scheffel"
    orcid         : "0000-0001-5963-9229"
    affiliation   : "1"
    corresponding : yes
    address       : "Zellescher Weg 17, 01069 Dresden, Germany"
    email         : "christoph_scheffel@tu-dresden.de"
    equal_contrib : yes
    role          :         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Methodology
      - Funding acquisition
      - Formal analysis
      - Investigation
      - Project administration
      - Software
      - Visualization
      - Writing - original draft preparation
      - Writing - review & editing
  - name          : "Josephine Zerna"
    orcid         : "0000-0003-2892-884X"
    affiliation   : "1"
    equal_contrib : yes
    role          :
      - Conceptualization
      - Methodology
      - Funding acquisition
      - Investigation
      - Project administration
      - Software
      - Visualization
      - Writing - review & editing
  - name          : "Anne Gärtner"
    orcid         : "0000-0003-4296-963X"
    affiliation   : "1"
    role          :
      - Formal analysis
      - Writing - review & editing
  - name          : "Denise Dörfel"
    orcid         :
    affiliation   : "1"
    role          :
      - Conceptuatlization
      - Writing - review & editing
  - name          : "Alexander Strobel"
    orcid         : "0000-0002-9426-5397"
    affiliation   : "1"
    role          :
      - Conceptualization
      - Writing - review & editing 
affiliation       :
  - id            : "1"
    institution   : "Faculty of Psychology, Technische Universität Dresden, 01069 Dresden, Germany"
authornote        :
abstract          : |
 Individuals have a repertoire of emotion regulation (ER) strategies at their disposal, which they can use more or less flexibly. 
 In ER flexibility research, strategies that facilitate goal achievement are considered adaptive and therefore are subjectively valuable. 
 Individuals are motivated to reduce their emotional arousal effectively and to avoid cognitive effort. 
 Perceived costs of ER strategies in the form of effort, however, are highly subjective. 
 Subjective values (SVs) should therefore represent a trade-off between effectiveness and subjectively required cognitive effort. 
 However, SVs of ER strategies have not been determined so far. 
 We present a paradigm that is suitable for determining individual SVs of ER strategies. 
 Using a multilevel modelling approach, it will be investigated whether individual SVs can be explained by effectiveness (subjective arousal, facial muscle activity) and subjective effort. 
 Relations of SVs to personality traits will be explored.
keywords          : "emotion regulation, regulatory effort, effort discounting, registered report, specification curve analysis"
wordcount         : "6289"
bibliography      : ["ER_ED.bib"]
floatsintext      : yes
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
csl               : nature.csl
header-includes   :
    - \usepackage{booktabs}
    - \usepackage{longtable}
    - \usepackage{array}
    - \usepackage{multirow}
    - \usepackage{wrapfig}
    - \usepackage{float}
    - \usepackage{colortbl}
    - \usepackage{pdflscape}
    - \usepackage{tabu}
    - \usepackage{threeparttable}
    - \usepackage{threeparttablex}
    - \usepackage[normalem]{ulem}
    - \usepackage{makecell}
    - \usepackage{xcolor}
    - \usepackage{setspace}\doublespacing
    - \usepackage[final]{pdfpages}
    - \usepackage{chngcntr}
editor_options: 
  markdown: 
    wrap: sentence
---

```{=tex}
\renewcommand\thesection{\Alph{section}}
\counterwithout{figure}{section}
\setcounter{figure}{0}
```

------------------------------------------------------------------------

```{r setupManuscript, echo=FALSE, message=FALSE, warning=FALSE}

library(knitr)
# set knitr options
knitr::opts_chunk$set(out.width = "\\textwidth")

# load libraries
library(here) # for path independent file referencing
# set top level directory to source file
here::i_am("flag_project_root_CAD.txt")

library(papaja) # APA conform output
library(kableExtra) # for tables in R Markdown
library(BayesFactor) # for bayes factors

# load workspace variables from analyses_ERED.R script
load(here("06_Paper","ER-ED","Workspace_ERED_pilot.RData"))

```{r child = "TheoreticalBackground_rev.Rmd"}
```

```{r child = "method_rev.Rmd"}
```

# References

```{=tex}
\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
```
::: {#refs custom-style="Bibliography"}
:::

```{=tex}
\endgroup
```
\newpage

# Acknowledgements

This research is partly funded by the German Research Foundation (DFG) as part of the Collaborative Research Center (CRC) 940.
Additionally, we have applied for funding of the participants' compensation from centralized funds of the Faculty of Psychology at Technische Universität Dresden.
Applications for the centralized funds will be reviewed in May.
Regardless of whether or not this additional funding will be granted, the study can commence immediately.
The funders have/had no role in study design, data collection and analysis, decision to publish or preparation of the manuscript.

# Competing Interests

The authors declare no competing interests.

```{=tex}
\newpage
\setcounter{figure}{0}
```
# Figures and figure captions

@@

INSERT FIGURE 1 HERE

*Figure 1.* Exemplary visualization of two response patterns.
In the top half, the person has a clear preference for one of the three strategies.
In the lower half, they have no clear preference and therefore show an inconsistent response pattern.
This pattern can also be represented by our paradigm.

INSERT FIGURE 2 HERE

*Figure 2.* Block design of the paradigm.
Every participant starts with two "active viewing" blocks containing neutral (Block 1) and negative (Block 2) pictures.
Order of the regulation blocks (Blocks 3, 4, and 5) is randomized between participants.
After, the discounting procedure takes place.
All three regulation strategies are pairwise compared.
Before the last block, participants can decide which regulation strategy they want to reapply.
Subjective arousal and effort ratings are assessed after each block using a slider on screen with a continuous scale.

# Design Table {#DesignTable}

\includepdf[pages={-}, landscape=true]{Supplement/Design_Table_T2.pdf}

INCLUDE SUPPLEMENT HERE

<!--
\includepdf[pages={-}, landscape=true]{Supplement/StimList_Suppl.pdf}
\counterwithin{figure}{section}
\counterwithin{table}{section}
\setcounter{section}{19}
\setcounter{figure}{0}
\setcounter{table}{1}
\newpage

@@

## Pilot study: Subjective arousal in the conditions "Active viewing - neutral" and "Active viewing - negative"

ANOVA:

`r afex::nice(SubjArousalView_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(extractBF(SubjArousalView_pilot_BF)$bf, digits = 2)`

Paired contrasts:

```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  SubjArousalView_pilot_con,
  caption = "Paired contrasts for the rmANOVA comparing subjective arousal of negative and neutral pictures in the condition \"active viewing\".",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
  escape = FALSE,
  placement = "H"
)
```

Figure:

```{r FigSubjArousalViewPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective arousal ratings for the conditions \"Active viewing - neutral\" and \"Active viewing - negative\" visualized as boxplots. Each dot represents the effort rating of a single subject. Bold dots represent outliers.", fig.pos="H", out.width="75%"}

print(FigSubjArousalViewPilot)
```

## Pilot study: Subjective arousal in the conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression"

ANOVA: `r afex::nice(SubjArousalReg_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(extractBF(SubjArousalReg_pilot_BF)$bf, digits = 2)`

Paired contrasts:

```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  SubjArousalReg_pilot_con,
  caption = "Paired contrasts for the rmANOVA comparing subjective arousal of conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\".",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
  escape = FALSE,
  placement = "H"
)
```

Figure:

```{r FigSubjArousalRegPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective arousal ratings for the conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\" visualized as boxplots. Each dot represents the effort rating of a single subject. Bold dots represent outliers.", fig.pos="H", out.width="75%"}

print(FigSubjArousalRegPilot)
```

## Pilot study: Physiological responding (*Corrugator* and *Levator* activity) in the conditions "Active viewing - neutral" and "Active viewing - negative"

*Corrugator*: ANOVA: `r afex::nice(EMGCorrView_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(extractBF(EMGCorrView_pilot_BF)$bf, digits = 2)`

Paired contrasts:

```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  EMGCorrView_pilot_con,
  caption = "Paired contrasts for the rmANOVA comparing physiological responding (Corrugator activity) of negative and neutral pictures in the condition \"active viewing\".",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
  escape = FALSE,
  placement = "H"
)
```

*Levator*: ANOVA: `r afex::nice(EMGLevView_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(extractBF(EMGLevView_pilot_BF)$bf, digits = 2)`

Paired contrasts:

```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  EMGLevView_pilot_con,
  caption = "Paired contrasts for the rmANOVA comparing physiological responding (Levator activity) of negative and neutral pictures in the condition \"active viewing\".",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
  escape = FALSE,
  placement = "H"
)
```

Figures:

```{r FigEMGCorrViewPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Corrugator activity for the conditions \"Active viewing - neutral\" and \"Active viewing - negative\" visualized as boxplots. Each dot represents the corrugator activity of a single trial. Bold dots represent outliers.", fig.pos="H", out.width="75%"}

print(FigEMGCorrViewPilot)
```

```{r FigEMGLevViewPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Levator activity for the conditions \"Active viewing - neutral\" and \"Active viewing - negative\" visualized as boxplots. Each dot represents the levator activity of a single trial. Bold dots represent outliers.", fig.pos="H", out.width="75%"}

print(FigEMGLevViewPilot)
```

## Pilot study: Physiological responding (*Corrugator* and *Levator* activity) in the conditions"Active viewing - negative", "Distraction", "Distancing", and "Suppression"

*Corrugator*: ANOVA: `r afex::nice(EMGCorrReg_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(extractBF(EMGCorrReg_pilot_BF)$bf, digits = 2)`

Paired contrasts:

```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  EMGCorrReg_pilot_con,
  caption = "Paired contrasts for the rmANOVA comparing physiological responding (Corrugator activity) of conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\".",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
  escape = FALSE,
  placement = "H"
)
```

*Levator*: ANOVA: `r afex::nice(EMGLevReg_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(extractBF(EMGLevReg_pilot_BF)$bf, digits = 2)`

Paired contrasts:

```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  EMGLevReg_pilot_con,
  caption = "Paired contrasts for the rmANOVA comparing physiological respodning (Levator activity) of conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\".",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
  escape = FALSE,
  placement = "H"
)
```

Figures:

```{r FigEMGCorrRegPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Corrugator activity for the conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\" visualized as boxplots. Each dot represents the corrugator activity of a single trial. Bold dots represent outliers.", fig.pos="H", out.width="75%"}

print(FigEMGCorrRegPilot)
```

```{r FigEMGLevRegPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Levator activity for the conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\" visualized as boxplots. Each dot represents the levator activity of a single trial. Bold dots represent outliers.", fig.pos="H", out.width="75%"}

print(FigEMGLevRegPilot)
```

## Pilot study: Subjective effort in the conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression"

ANOVA: `r afex::nice(SubjEffort_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(extractBF(SubjEffort_pilot_BF)$bf, digits = 2)`

Paired contrasts:

```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  SubjEffort_pilot_con,
  caption = "Paired contrasts for the rmANOVA comparing subjective effort of conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\".",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
  escape = FALSE,
  placement = "H"
)
```

Figure:

```{r FigSubjEffortPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective effort ratings for the conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\" visualized as boxplots. Each dot represents the effort rating of a single subject. Bold dots represent outliers.", fig.pos="H", out.width="75%"}

print(FigSubjEffortPilot)
```
-->

>>>>

---
title: "Supplement"
author: "Christoph Scheffel"
date: "2023-02-16"
output: html_document
---

```{r SetupSupplement, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(here)       # to set directories without defined paths
# set top level directory to source file
here::i_am("flag_project_root_CAD.txt")

library(tidyverse)

# load workspace variables from analyses_ERED.R script
base::load(here("06_Paper","ER-ED","ERED_Stage2","Workspace_ERED_pilot.RData"))
base::load(here("06_Paper","ER-ED","ERED_Stage2","Workspace_ERED.RData"))
```

\includepdf[pages={-}, landscape=true]{Supplement/StimList_Suppl.pdf}
\counterwithin{figure}{section}
\counterwithin{table}{section}
\setcounter{section}{19}
\setcounter{figure}{0}
\setcounter{table}{1}

@@

@@

## Test for normal distribution of predictor variables

``` {r TabNV, echo=FALSE, message=FALSE, warning=FALSE}

papaja::apa_table(
  df.NV.subj,
  caption = "Results of Shapiro-Wilk test for normal distribution of subjective arousal and effort ratings for all strategies.",
  escape = FALSE)

papaja::apa_table(
  df.NV.EMG,
  caption = "Results of Shapiro-Wilk test for normal distribution of *Corrugator* and *Levator* activity for all strategies.",
  escape = FALSE)
